---
title: "IML"
author: "Yiming Tan, yt2633"
date: "April 20, 2019"
output: 
  pdf_document: 
    fig_height: 3.5
    fig_width: 4.5
---

#Data and Model

Fit the model on Boston housing dataset to predict the median values

```{r}
data("Boston", package  = "MASS")
head(Boston)
```

```{r, warning=FALSE}
#install.packages("iml")
#library("randomForest")
library("iml")
library("randomForest")
set.seed(2019)
rf = randomForest(medv ~ ., data = Boston, ntree = 1000, mtry = 4)
```


```{r}
X = Boston[which(names(Boston) != "medv")]
predictor = Predictor$new(rf, data = X, y = Boston$medv)
```

#Feature importance obtained by the permutation algorithm

```{r}
imp = FeatureImp$new(predictor, loss = "mae")
plot(imp)
```

#Feature effects (ALE or PDP)

```{r}
ale = FeatureEffect$new(predictor, feature = "lstat",method = "ale",grid.size = 20)
ale$plot()
pdp = FeatureEffect$new(predictor, feature = "lstat",method = "pdp",grid.size = 20)
pdp$plot()
```

```{r}
ale$set.feature("age")
ale$plot()
```

```{r}
effs = FeatureEffects$new(predictor)
plot(effs)
```

#Global Surrogate Model (Tree-based)

```{r}
tree_sur = TreeSurrogate$new(predictor,maxdepth = 2)
plot(tree_sur)
```

```{r}
tree_sur = TreeSurrogate$new(predictor,maxdepth = 3)
plot(tree_sur)
```

#Local Surrogate Model

LocalModel fits locally weighted linear regression models to explain the indiviual predictions.

```{r,warning=FALSE}
loc = LocalModel$new(predictor, X[1,], k = 5)
print(loc)
plot(loc)
```

# Shapley Value

The contribution of a feature value to the difference between the actual prediction and the mean prediction


```{r}
shapley = Shapley$new(predictor, X[1,])
print(shapley)
plot(shapley)
```

